Magnetized accretion disks around Kerr black holes with scalar hair - I. Constant angular momentum disks

### 2018-08-03 paper_prd.tex
Some work on the draft.

\begin{figure*}
\centering
\includegraphics[scale=0.14]{figures/fig3_I_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig3_I_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig3_I__10.pdf}
\\
\includegraphics[scale=0.14]{figures/fig3_II_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig3_II_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig3_II__10.pdf}
\\
\includegraphics[scale=0.14]{figures/fig3_III_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig3_III_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig3_III__10.pdf}
\\
\includegraphics[scale=0.14]{figures/fig3_IV_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig3_IV_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig3_IV__10.pdf}
\hspace{-0.2cm}
\caption{Rest-mass density distribution using perimeteral coordinates. From top to bottom the rows correspond to the different models for the KBHsSH (I, II, III and IV). From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
\label{models_peri_I}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.14]{figures/fig4_V_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig4_V_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig4_V__10.pdf}
\\
\includegraphics[scale=0.14]{figures/fig4_VI_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig4_VI_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig4_VI__10.pdf}
\\
\includegraphics[scale=0.14]{figures/fig4_VII_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig4_VII_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig4_VII__10.pdf}
\hspace{-0.2cm}
\caption{Rest-mass density distribution using perimeteral coordinates. From top to bottom the rows correspond to the different models for the KBHsSH (V, VI, VII). From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
\label{models_peri_II}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.12]{figures/fig5_I_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.12]{figures/fig5_IV_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.12]{figures/fig5_VII_10.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.12]{figures/fig5_I__10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.12]{figures/fig5_IV__10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.12]{figures/fig5_VII__10.pdf}
\hspace{-0.2cm}
\caption{Gravitational mass density distribution for the torus $\rho_{\mathrm{T}}$ (up) and the scalar field $\rho_{\mathrm{SF}}$ (down). From left to right the columns correspond to different models (I, IV and VII). From top to bottom, the rows correspond to different calues of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
\label{comparison_mass_density}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.12]{figures/fig6_I_10.pdf}
\hspace{-0.4cm}
\includegraphics[scale=0.12]{figures/fig6_IV_10.pdf}
\hspace{-0.4cm}
\includegraphics[scale=0.12]{figures/fig6_VII_10.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.12]{figures/fig6_I__10.pdf}
\hspace{-0.4cm}
\includegraphics[scale=0.12]{figures/fig6_IV__10.pdf}
\hspace{-0.4cm}
\includegraphics[scale=0.12]{figures/fig6_VII__10.pdf}
\hspace{-0.2cm}
\caption{Gravitational mass density distribution for the torus $\rho_{\mathrm{T}}$ (up) and the scalar field $\rho_{\mathrm{SF}}$ (down) using perimeteral coordinates. From left to right the columns correspond to different models (I, IV and VII). From top to bottom, the rows correspond to different calues of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
\label{comparison_mass_density_peri}
\end{figure*}

@@

\tf{We also have to emphasize that we do not fix $h=1$.}

@@

@@

In figures~\ref{models_peri_I} and~\ref{models_peri_II} we show the same models, but using a perimetral radial coordinate such as $R = e^{F_2} r$. \tf{We need to justify why we introduce this new radial coordinate. What is the benefit?}

@@

Tables~\ref{HBH_disk_parameters} and~\ref{KBH_disk_parameters} show the relevant physical quantities for both KBHSH and the same KBH cases we presented in the figures. First of all, it is worth to mention that KBHsSH can violate the Kerr bound for the potential $\Delta W \equiv W_{\mathrm{in}} - W_{\mathrm{c}}$. As shown in~\cite{Abramowicz:1978}, constant angular momentum disks exhibit a maximum for $|\Delta W|$ when the spin parameter $a$ approaches 1. This value is $\Delta W_{\mathrm{max}} = -\frac{1}{2} \ln 3 \simeq -0.549$. The models V, VI and VII violate that bound. This is related, as we will see, with the maximum value of the specific enthalpy, pressure and magnetic pressure.

In figure~\ref{comparison_mass_density} we show the total energy density of the torus $\rho_{\mathrm{T}}$ (superior half) and the total energy density of the scalar field $\rho_{\mathrm{SF}}$ for 3 of the models (I, IV and VII) and 2 values of the magnetization parameter at the center ($10^{10}$ and $10^{-10}$). In figure~\ref{comparison_mass_density_peri}, we show the same, but using the perimeteral coordinate we defined earlier. The plots show that the maximum of the total energy density of the disk $\rho_{\mathrm{t}}$ is closer to the maximum of the total energy density of the scalar field $\rho_{\mathrm{SF}}$ for increasing hair.

@@

\begin{table*}[t]
\caption{Disk parameters and values of their relevant physical magnitudes. For all the cases, we have $R_{\mathrm{in}} = R_{\mathrm{mb}}$ and $l = l_{\mathrm{mb}}$}        
\label{HBH_disk_parameters}      
\centering          
\begin{tabular}{c c c c c  c c c c c c c}
\hline\hline       
 Model & $l$ & $W_{\mathrm{c}}$ & $R_{\mathrm{in}}$ & $R_{\mathrm{c}}$ &  $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $h_{\mathrm{max}}$ & $\rho_{\mathrm{max}}$ & $p_{\mathrm{max}}$ & $p_{\mathrm{m, max}}$ & $R_{\mathrm{max}}$ & $R_{\mathrm{m, max}}$\\ 
\hline           
I & $0.934$ & $-0.188$ & $0.81$ & $1.14$ & $10^{10}$ & $1.21$ & $1.0$ & $5.16 \times 10^{-2}$ & $5.50 \times 10^{-12}$ & $1.14$ & $1.26$\\ 
 \hline 
 &  &  &  &  & $1$ & $1.10$ & $1.17$ & $3.11 \times 10^{-2}$ & $2.68 \times 10^{-2}$ & $1.01$ & $1.06$\\ 
 \hline 
 &  &  &  &  & $10^{-10}$ & $1.0$ & $1.90$ & $1.10 \times 10^{-11}$ & $7.80 \times 10^{-2}$ & $0.93$ & $0.96$\\ 
 \hline 
II & $0.933$ & $-0.205$ & $0.75$ & $1.18$ & $10^{10}$ & $1.23$ & $1.0$ & $5.69 \times 10^{-2}$ & $6.14 \times 10^{-12}$ & $1.18$ & $1.36$\\ 
 \hline 
 &  &  &  &  & $1$ & $1.12$ & $1.19$ & $3.50 \times 10^{-2}$ & $2.97 \times 10^{-2}$ & $1.00$ & $1.07$\\ 
 \hline 
 &  &  &  &  & $10^{-10}$ & $1.0$ & $2.01$ & $1.30 \times 10^{-11}$ & $8.99 \times 10^{-2}$ & $0.91$ & $0.94$ \\ 
 \hline 
III & $1.06$ & $-0.362$ & $0.84$ & $1.07$ & $10^{10}$ & $1.44$ & $1.0$ & $0.109$ & $1.21 \times 10^{-11}$ & $1.07$ & $1.22$\\ 
 \hline 
 &  &  &  &  & $1$ & $1.23$ & $1.28$ & $7.22 \times 10^{-2}$ & $5.76 \times 10^{-2}$ & $0.95$ & $0.99$ \\ 
 \hline 
 &  &  &  &  & $10^{-10}$ & $1.0$ & $2.74$ & $3.48 \times 10^{-11}$ & $0.206$ & $0.89$ & $0.91$\\ 
\hline  
IV & $1.16$ & $-0.547$ & $0.67$ & $1.06$ & $10^{10}$ & $1.723$ & $1.0$ & $0.182$ & $2.09 \times 10^{-11}$ & $1.06$ & $1.34$ \\ 
\hline 
 &  &  &  &  & $1$ & $1.38$ & $1.37$ & $0.129$ & $9.76 \times 10^{-2}$ & $0.85$ & $0.91$\\ 
\hline 
 &  &  &  &  & $10^{-10}$ & $1.0$ & $3.70$ & $7.83 \times 10^{-11}$ & $0.408$ & $0.76$ & $0.78$ \\ 
\hline   
V & $1.20$ & $-0.685$ & $0.58$ & $1.07$ & $10^{10}$ & $1.98$ & $1.0$ & $0.246$ & $2.76 \times 10^{-11}$ & $1.07$ & $1.31$\\ 
\hline 
 &  &  &  &  & $1$ & $1.51$ & $1.40$ & $0.178$ & $0.132$ & $0.78$ & $0.87$ \\ 
\hline 
 &  &  &  &  & $10^{-10}$ & $1.0$ & $4.26$ & $1.18 \times 10{-10}$ & $0.579$ & $0.67$ & $0.69$ \\ 
\hline   
VI & $1.20$ & $-0.832$ & $0.43$ & $1.12$ & $10^{10}$ & $2.30$ & $1.0$ & $0.324$ & $3.52 \times 10^{-11}$ & $1.12$ & $1.32$ \\ 
\hline 
 &  &  &  &  & $1$ & $1.66$ & $1.39$ & $0.228$ & $0.169$ & $0.72$ & $0.86$ \\ 
\hline 
 &  &  &  &  & $10^{-10}$ & $1.0$ & $4.54$ & $1.57 \times 10^{-10}$ & $0.740$ & $0.55$ & $0.59$ \\ 
\hline 
VII & $0.920$ & $-1.236$ & $0.18$ & $1.10$ & $10^{-10}$ & $3.44$ & $1.0$ & $0.610$ & $6.459 \times 10^{-11}$ & $1.10$ & $1.25$ \\ 
\hline 
 &  &  &  &  & $1$ & $2.25$ & $1.64$ & $0.510$ & $0.322$ & $0.43$ & $0.62$\\ 
\hline 
 &  &  &  &  & $10^{-10}$ & $1.0$ & $10.42$ & $7.03 \times 10^{-10}$ & $2.44$ & $0.28$ & $0.30$\\ 
\hline 
\end{tabular}
\end{table*}

>>>>

\begin{figure*}
\centering
\includegraphics[scale=0.14]{figures/fig3_I_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig3_I_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig3_I__10.pdf}
\\
\includegraphics[scale=0.14]{figures/fig3_II_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig3_II_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig3_II__10.pdf}
\\
\includegraphics[scale=0.14]{figures/fig3_III_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig3_III_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig3_III__10.pdf}
\\
\includegraphics[scale=0.14]{figures/fig3_IV_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig3_IV_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig3_IV__10.pdf}
\hspace{-0.2cm}
\caption{Same as Fig.~\ref{models_I} but using the perimetral radial coordinate $R$. \tf{Same comment as in the previous figure.}}
\label{models_peri_I}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.14]{figures/fig4_V_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig4_V_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig4_V__10.pdf}
\\
\includegraphics[scale=0.14]{figures/fig4_VI_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig4_VI_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig4_VI__10.pdf}
\\
\includegraphics[scale=0.14]{figures/fig4_VII_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig4_VII_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig4_VII__10.pdf}
\hspace{-0.2cm}
\caption{Same as Fig.~\ref{models_II} but using the perimetral radial coordinate $R$. \tf{Same comment as in the previous figure.}}
\label{models_peri_II}
\end{figure*}

@@

\tf{We also have to emphasize somewhere in the paper that we do not fix $h=1$. This is an important difference with respect to the work of~\cite{Vincent:2016}.}

@@

\begin{table*}[t]
\caption{Values of the relevant physical magnitudes of our models of magnetized, equilibrium tori around KBHsSH. For all cases,  $R_{\mathrm{in}} = R_{\mathrm{mb}}$ and $l = l_{\mathrm{mb}}$. \tf{Are we using the perimetral radial coordinate in this table?}}       
\label{HBH_disk_parameters}      
\centering          
\begin{tabular}{c c c c c  c c c c c c c}
\hline\hline       
 Model & $l$ & $W_{\mathrm{c}}$ & $R_{\mathrm{in}}$ & $R_{\mathrm{c}}$ &  $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $h_{\mathrm{max}}$ & $\rho_{\mathrm{max}}$ & $p_{\mathrm{max}}$ & $p_{\mathrm{m, max}}$ & $R_{\mathrm{max}}$ & $R_{\mathrm{m, max}}$\\ 
\hline           
I & $0.934$ & $-0.188$ & $0.81$ & $1.14$ & $10^{10}$ & $1.21$ & $1.0$ & $5.16 \times 10^{-2}$ & $5.50 \times 10^{-12}$ & $1.14$ & $1.26$\\ 
 \hline 
 &  &  &  &  & $1$ & $1.10$ & $1.17$ & $3.11 \times 10^{-2}$ & $2.68 \times 10^{-2}$ & $1.01$ & $1.06$\\ 
 \hline 
 &  &  &  &  & $10^{-10}$ & $1.0$ & $1.90$ & $1.10 \times 10^{-11}$ & $7.80 \times 10^{-2}$ & $0.93$ & $0.96$\\ 
 \hline 
II & $0.933$ & $-0.205$ & $0.75$ & $1.18$ & $10^{10}$ & $1.23$ & $1.0$ & $5.69 \times 10^{-2}$ & $6.14 \times 10^{-12}$ & $1.18$ & $1.36$\\ 
 \hline 
 &  &  &  &  & $1$ & $1.12$ & $1.19$ & $3.50 \times 10^{-2}$ & $2.97 \times 10^{-2}$ & $1.00$ & $1.07$\\ 
 \hline 
 &  &  &  &  & $10^{-10}$ & $1.0$ & $2.01$ & $1.30 \times 10^{-11}$ & $8.99 \times 10^{-2}$ & $0.91$ & $0.94$ \\ 
 \hline 
III & $1.060$ & $-0.362$ & $0.84$ & $1.07$ & $10^{10}$ & $1.44$ & $1.0$ & $0.109$ & $1.21 \times 10^{-11}$ & $1.07$ & $1.22$\\ 
 \hline 
 &  &  &  &  & $1$ & $1.23$ & $1.28$ & $7.22 \times 10^{-2}$ & $5.76 \times 10^{-2}$ & $0.95$ & $0.99$ \\ 
 \hline 
 &  &  &  &  & $10^{-10}$ & $1.0$ & $2.74$ & $3.48 \times 10^{-11}$ & $0.206$ & $0.89$ & $0.91$\\ 
\hline  
IV & $1.160$ & $-0.547$ & $0.67$ & $1.06$ & $10^{10}$ & $1.723$ & $1.0$ & $0.182$ & $2.09 \times 10^{-11}$ & $1.06$ & $1.34$ \\ 
\hline 
 &  &  &  &  & $1$ & $1.38$ & $1.37$ & $0.129$ & $9.76 \times 10^{-2}$ & $0.85$ & $0.91$\\ 
\hline 
 &  &  &  &  & $10^{-10}$ & $1.0$ & $3.70$ & $7.83 \times 10^{-11}$ & $0.408$ & $0.76$ & $0.78$ \\ 
\hline   
V & $1.200$ & $-0.685$ & $0.58$ & $1.07$ & $10^{10}$ & $1.98$ & $1.0$ & $0.246$ & $2.76 \times 10^{-11}$ & $1.07$ & $1.31$\\ 
\hline 
 &  &  &  &  & $1$ & $1.51$ & $1.40$ & $0.178$ & $0.132$ & $0.78$ & $0.87$ \\ 
\hline 
 &  &  &  &  & $10^{-10}$ & $1.0$ & $4.26$ & $1.18 \times 10{-10}$ & $0.579$ & $0.67$ & $0.69$ \\ 
\hline   
VI & $1.200$ & $-0.832$ & $0.43$ & $1.12$ & $10^{10}$ & $2.30$ & $1.0$ & $0.324$ & $3.52 \times 10^{-11}$ & $1.12$ & $1.32$ \\ 
\hline 
 &  &  &  &  & $1$ & $1.66$ & $1.39$ & $0.228$ & $0.169$ & $0.72$ & $0.86$ \\ 
\hline 
 &  &  &  &  & $10^{-10}$ & $1.0$ & $4.54$ & $1.57 \times 10^{-10}$ & $0.740$ & $0.55$ & $0.59$ \\ 
\hline 
VII & $0.920$ & $-1.236$ & $0.18$ & $1.10$ & $10^{-10}$ & $3.44$ & $1.0$ & $0.610$ & $6.459 \times 10^{-11}$ & $1.10$ & $1.25$ \\ 
\hline 
 &  &  &  &  & $1$ & $2.25$ & $1.64$ & $0.510$ & $0.322$ & $0.43$ & $0.62$\\ 
\hline 
 &  &  &  &  & $10^{-10}$ & $1.0$ & $10.42$ & $7.03 \times 10^{-10}$ & $2.44$ & $0.28$ & $0.30$\\ 
\hline 
\end{tabular}
\end{table*}

@@

In figures~\ref{models_peri_I} and~\ref{models_peri_II} we show the same models, but using a perimetral radial coordinate such as $R = e^{F_2} r$. \tf{We need to justify why we introduce this new radial coordinate. What is the benefit? Please include an explanation and also describe briefly the differences/similarities between these two figures and the first two.}

@@

Table~\ref{HBH_disk_parameters} reports the relevant physical quantities for our disk models around KBHsSH. First of all, it is worth to mention that KBHsSH can violate the Kerr bound for the potential $\Delta W \equiv W_{\mathrm{in}} - W_{\mathrm{c}}$. As shown in~\cite{Abramowicz:1978}, constant angular momentum disks exhibit a maximum for $|\Delta W|$ when the spin parameter $a$ approaches 1. This value is $\Delta W_{\mathrm{max}} = -\frac{1}{2} \ln 3 \simeq -0.549$. The models V, VI and VII violate that bound. This is related, as we will see, with the maximum value of the specific enthalpy, pressure and magnetic pressure.

\begin{figure*}
\centering
\includegraphics[scale=0.12]{figures/fig5_I_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.12]{figures/fig5_IV_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.12]{figures/fig5_VII_10.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.12]{figures/fig5_I__10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.12]{figures/fig5_IV__10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.12]{figures/fig5_VII__10.pdf}
\hspace{-0.2cm}
\caption{Energy density distribution for the torus $\rho_{\mathrm{T}}$ (upper half of the images) and for the scalar field $\rho_{\mathrm{SF}}$ (lower half). From left to right the columns correspond to models I, IV, and VII. The top row corresponds to non-magnetized models ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$) and the bottom row to strongly magnetized models ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$).
\tf{I think there is a lot of vertical space that we do not really need in these plots. To save some space, as we have many figures, I suggest to plot the vertical axis in shorter ranges, say $[-0.75,0.75]$ for model I, $[-0.5,0.5]$ for model IV, and $[-0.35,0.35]$ for model VII (and keeping the horizontal axis as it is now). I know the plot will not look squared, but that's fine.}
}
\label{comparison_mass_density}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.12]{figures/fig6_I_10.pdf}
\hspace{-0.4cm}
\includegraphics[scale=0.12]{figures/fig6_IV_10.pdf}
\hspace{-0.4cm}
\includegraphics[scale=0.12]{figures/fig6_VII_10.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.12]{figures/fig6_I__10.pdf}
\hspace{-0.4cm}
\includegraphics[scale=0.12]{figures/fig6_IV__10.pdf}
\hspace{-0.4cm}
\includegraphics[scale=0.12]{figures/fig6_VII__10.pdf}
\hspace{-0.2cm}
\caption{Same as Fig.~\ref{comparison_mass_density} but using the perimetral radial coordinate. \tf{Same comment as in the previous figure regarding the vertical range, in this case $[-1.5,1.5]$ for all models.}}
\label{comparison_mass_density_peri}
\end{figure*}

Table~\ref{KBH_disk_parameters} reports the relevant physical quantities for the disks built around KBH. \tf{Describe.}

In figure~\ref{comparison_mass_density} we show the total energy density of the torus $\rho_{\mathrm{T}}$ (upper half of each image) and the total energy density of the scalar field $\rho_{\mathrm{SF}}$ (lower half) for models I, IV and VII and 2 values of the magnetization parameter at the center ($10^{10}$, left panel, and $10^{-10}$, right panel). \tf{Describe this figure.}

In figure~\ref{comparison_mass_density_peri}, we show the same, but using the perimeteral coordinate we defined earlier. The plots show that the maximum of the total energy density of the disk $\rho_{\mathrm{t}}$ is closer to the maximum of the total energy density of the scalar field $\rho_{\mathrm{SF}}$ for increasing hair. \tf{This trend is only satisfied for the unmagnetized models (top row) but not for the strongly magnetized models.}

\tf{One question: in our approach we are building the disks using the stress-energy tensor of the fluid only. Is this correct? Shouldn't we consider the entire stress-energy tensor from the fluid and the scalar field? Is this a valid approximation because we are in the test-fluid regime? What did~\cite{Vincent:2016} do?}

@@
